Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-09 ms.tex
working to fix captions for reddening residual plots

\subsubsection{Absolute Zero Level}
\label{sec:zp_abs}
In \cite{planckdust}, the absolute zero level of thermal dust emission was set 
by requiring that \PLANCK~infrared emission tends to zero when H\,\textsc{i} is
zero, assuming a linear correlation between these two measurements at low 
column density. However, this approach is somewhat unsatisfying in that there 
appear to be different slopes of \PLANCK~857 GHz versus H\,\textsc{i} for 
different ranges of H\,\textsc{i} intensity. In particular, \PLANCK~857 GHz 
appears to ``flatten out'' at very low H\,\textsc{i}. More quantitavely, we 
have found using the LAB H\,\textsc{i} data \citep{lab} for 
$-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for H\,\textsc{i}$<$70 K km/s
is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
$<$H\,\textsc{i}$<$200 K km/s, and as a result the implied zero-point offsets 
for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid.eps, width=6.6in}
\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$. The grayscale represents the conditional probability within each
bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
and lower black lines represent the moving 75th and 25th percentiles 
respectively.}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
\caption{\label{fig:resid_ecl} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$. The 
grayscale represents the conditional probability within each bin in SFD 
$E(B-V)$. The central black line shows the moving median. The upper and lower 
black lines represent the moving 75th and 25th percentiles respectively.}
\end{center}
\end{figure*}

>>>>

\subsubsection{Absolute Zero Level}
\label{sec:zp_abs}
In \cite{planckdust}, the absolute zero level of thermal dust emission was set 
by requiring that \PLANCK~infrared emission tends to zero when H\,\textsc{i} is
zero, assuming a linear correlation between these two measurements at low 
column density. However, this approach is somewhat unsatisfying in that there 
appear to be different slopes of \PLANCK~857 GHz versus H\,\textsc{i} for 
different ranges of H\,\textsc{i} intensity. In particular, \PLANCK~857 GHz 
appears to ``flatten out'' at very low H\,\textsc{i}. More quantitavely, we 
have found using the LAB H\,\textsc{i} data \citep{lab} for 
$-72$$<$$v_{LSR}$$<$$+25$ km/s that the best-fit slope for H\,\textsc{i}$<$70 K
km/s is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
$<$H\,\textsc{i}$<$200 K km/s, and as a result the implied zero-point offsets 
for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid.eps, width=6.6in}
\caption{\label{fig:resid} (top left) Residuals of $E(B-V)_{2comp}$ relative to
$E(B-V)_{SSPP}$ as a function of $E(B-V)_{SFD}$. The grayscale represents the 
conditional probability within each $E(B-V)_{SFD}$ bin. The central black line 
shows the moving median. The upper and lower black lines represent the moving 
75th and 25th percentiles respectively. (bottom left) Residuals of 
$E(B-V)_{2comp}$ relative to $E(B-V)_{SSPP}$ as a function of hot dust 
temperature $T_2$. (top right) Same as top left, but illustrating the residuals
of $E(B-V)_{mbb}$, our calibration of the \cite{planckdust} $\tau_{353}$ to 
$E(B-V)_{SSPP}$. (bottom right)  Same as bottom left, but showing the 
$E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
\cite{planckdust}.}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
\caption{\label{fig:resid_ecl} Same as Figure \ref{fig:resid}, but 
restricting to high ecliptic latitude, $|\beta|>20^{\circ}$. The top left and 
top right plots both show that the bending of the reddening residuals as a 
function of $E(B-V)_{SFD}$ as seen in Figure \ref{fig:resid} has been 
eliminated. Further, the two-component reddening residual temperature 
dependence (bottom left) has been significantly reduced relative to the
corresponding trend shown in Figure \ref{fig:resid}, bottom left panel.}
\end{center}
\end{figure*}
